\section*{Preface}
This is a report on USB Oscilloscope, submitted to the department of Electronics and Communication Engineering, Pulcowk Lalitpur. This report primarily describes the project in plain language intended for general reader in mind. 


Our project in the final completed form is intended to general users whose concern is only the output waveform and not on the technical details of the components involved and the software programming. We have tried to avoid the techical details of the software.


The software interface is made simple as possible to allow the general user understand it quickly and be able to use freely in no time. We have tried to make the user interface as close to the actual oscilloscope as possible.


In the very beginning we had plans in mind to make the oscilloscope out of a old CRT TV but after quite a exploration and brain stroming we concluded that we would better be making the oscilloscope based on USB and not on the CRT TV. 


We are especially thankful to Mr.Sumit Bam Shrestha for providing us with ecouragements and invaluable suggestions in the very beginning.


We would also like to thank all our friends, without whose help this project would not have been a success. We would like extend our sincere gratitude and respect to Dr. Diwakar Raj Panta and Dr. Ram Krishna Maharjan--the concerned teachers for handling this minor project of 068BEX. Also we would like to thank the department of Electronics and Computer Engineering, Pulchowk campus for encouraging us to accomplish this project.