\documentclass[aspectratio=169]{beamer}
\usetheme{AnnArbor}
\setbeamertemplate{navigation symbols}[default]
\usepackage{pgfpages}

%\useinnertheme{rectangles}

%\pgfpagesuselayout{4 on 1}[letterpaper,landscape,border shrink=5mm]
\usecolortheme{rose}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{graphicx}



\author{Madhav Humagain\\ Prakash Gautam\\}
\title{Life of a Student\\ And the way Forward}
\setbeamercovered{transparent} 
\setbeamertemplate{navigation symbols}{} 

%\logo{} 
%\institute{IOE Pulchowk Campus} 

\date{\today} 
\subject{Physics} 

\begin{document}
 
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}
\newpage

\section{Introduction}
\begin{frame}{Introduction}


\begin{itemize}
\item USB Based Oscilloscope.
\pause
\item Converts analog signal to digital, sends them to PC and
\pause
\item Displays The waveform in computer screen.
\pause
\end{itemize}
\end{frame}


\section{Objectives}
\begin{frame}
\frametitle{Objectives}
\framesubtitle{Why is the project being carried out?}

\begin{enumerate}
\item<1-> To accomplish the IOE course requirement.
\item<2-> To integrate hardware and software firmly.
\item<3-> To make life easy for students and researchers providing them with cheap oscilloscope.
\item<4-> Make a useful embeded system, not just a project for shake of project
\end{enumerate}
\uncover<5-> {To increase team collabration and carry out group project }
\end{frame}


\section{Features}
\begin{frame}
	\frametitle{What is so special about this oscilloscope?}
	\begin{block}{Answered Questions}
		How many primes are there?
	\end{block}
	
	\begin{block}{Open Questions}
Is every even number the sum of two primes?
\end{block}
\end{frame}
\section{Software Selection}
\begin{frame}
\frametitle{What’s Still To Do?}
\begin{columns}
\column{.5\textwidth}
\begin{block}{Answered Questions}
How many primes are there?
\end{block}
\column{.5\textwidth}
\begin{block}{Open Questions}
Is every even number the sum of two primes?
\end{block}
\end{columns}
\end{frame}

\section{Works Completed}
\begin{frame}[fragile]
\frametitle{An Algorithm For Finding Primes Numbers.}
\begin{verbatim}
int main (void)
{
    std::vector<bool> is_prime (100, true);
    for (int i = 2; i < 100; i++)
    if (is_prime[i])
    {
        std::cout << i << " ";
        for (int j=i;j<100;is_prime[j]=false, j+=i);
    }
    return 0;
}
\end{verbatim}
\begin{uncoverenv}<2>
Note the use of \verb|std::|.
\end{uncoverenv}
\end{frame}
\section{Budgets}
\begin{frame}[fragile]
\frametitle{An Algorithm For Finding Primes Numbers.}
\begin{semiverbatim}
\uncover<1->{\alert<0>{int main (void)}}
\uncover<1->{\alert<0>{\{}}
\uncover<1->{\alert<1>{ \alert<4>{std::}vector<bool> is_prime (100, true);}}
\uncover<1->{\alert<1>{ for (int i = 2; i < 100; i++)}}
\uncover<2->{\alert<2>{
if (is_prime[i])}}
\uncover<2->{\alert<0>{
\{}}
\uncover<3->{\alert<3>{
\alert<4>{std::}cout << i << " ";}}
\uncover<3->{\alert<3>{
for (int j = i; j < 100;}}
\uncover<3->{\alert<3>{
is_prime [j] = false, j+=i);}}
\uncover<2->{\alert<0>{
\}}}
\uncover<1->{\alert<0>{ return 0;}}
\uncover<1->{\alert<0>{\}}}
\end{semiverbatim}
\visible<4->{Note the use of \alert{\texttt{std::}}.}
\end{frame}

\section{Conclusion}
\begin{frame}
Shown on first slide.
\onslide<2-3>
Shown on second and third slide.
\begin{itemize}
\item
Still shown on the second and third slide.
\onslide+<4->
\item
Shown from slide 4 on.
\end{itemize}
Shown from slide 4 on.
\onslide
Shown on all slides.
\end{frame}
\end{document}